---
title: "p8105_hw5_yw4199"
author: "Yaduo Wang"
date: "2023-11-13"
output: github_document
---

```{r}
library(tidyverse)
library(broom)

# Setting options. 
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

```{r}
#get names of all files
file_name_list = list.files(path = "data", pattern = "*.csv", full.names = TRUE)

#Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
file_name_df = data_frame(file_name_list)
file_df = 
  file_name_df |> 
  map_dfr(read_csv) |> 
  mutate(subject_id = substring(file_name_list, 10, 11),
           arm = substring(file_name_list, 6, 8)) |> 
  mutate(
    arm = 
      case_match(
        arm, 
        "con" ~ "control", 
        "exp" ~ "experiment")) |> 
  relocate(arm, subject_id) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    values_to = "value") |> 
  mutate(week = substring(week, 6,6))
  
```

```{r}
# Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
file_df |> 
  group_by(arm, subject_id) |> 
  ggplot(aes(x = week, y = value, 
             group = subject_id, 
             color = interaction(arm, subject_id))) +
  geom_line() +
  facet_grid(~arm) +
  labs(title = "Observations Over Time",
       x = "Week", y = "Observation Values", color = "Arms") +
  theme_minimal()
```

Experimental groups have higher oberservational values overall compared to the control group over time. Moreover, the experimental group shows an overall increasing trend, compared to the more constant trend in the control group over time. 

## Problem 3
```{r}
set.seed(1)
```

```{r}
#Set the design elements. 
n = 30
sigma = 5
alpha = 0.05
true_mu_values = c(0, 1, 2, 3, 4, 5, 6)
datasets_number = 5000
```

```{r}
# Create output list.
power = vector("list", length = 0)
estimate_result = vector("list", length = 0)
estimate_rejected_null = vector("list", length = 0)

# T-test
t_test_function = function(true_mu) {
  data = rnorm(n, mean = true_mu, sd = sigma)
  
  test_result = broom::tidy(t.test(data, mu = 0))
  return(c(pull(test_result,estimate), 
           pull(test_result,p.value)))
  }

# Simulation
for (i in 0:6) {
  results = replicate(datasets_number, t_test_function(i))
  
  estimate = results[1, ]
  
  p_value = results[2, ]
  
  power[[as.character(i)]] = mean(p_value < alpha)
  estimate_result[[as.character(i)]] = mean(estimate)
  estimate_rejected_null[[as.character(i)]] = mean(estimate[p_value < alpha])
  }
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis.
 
```{r}
power_df = data.frame(true_mu = true_mu_values, power = unlist(power))
power_df |> 
  ggplot(aes(x = true_mu, y = power)) +
  geom_line() + 
  labs(title = "Power of the Test over True Mean",
       x = "True mean", y = "Power of the test") +
  theme_minimal()
```

From the graph, we can see that as the mean increases, the power of the test increases. 

Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis.
```{r}
estimate_result_df = data.frame(true_mu = true_mu_values, estimate_result = unlist(estimate_result))
estimate_result_df |> 
  ggplot(aes(x = true_mu, y = estimate_result)) +
  geom_line() + 
  labs(title = "Average Estimate of μ over True Mean",
       x = "True mean", y = "Average Estimate of μ") +
  theme_minimal()
```

Make a second plot the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. 

```{r}
estimate_rejected_null_df = data.frame(true_mu = true_mu_values, estimate_rejected_null = unlist(estimate_rejected_null))
estimate_rejected_null_df |> 
  ggplot(aes(x = true_mu, y = estimate_rejected_null)) +
  geom_line() + 
  labs(title = "Average Estimate in Samples with Rejected Null over True Mean",
       x = "True mean", 
       y = "Average Estimate in Samples with Rejected Null") +
  theme_minimal()
```

No, according to the two graphs, those two lines are not equal. The group with samples which rejected the null have higher values, since it does not contain 0 in their confidence interval. 
